\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-05-23 doc/manuscript.tex
intermediate changes

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_change_plus_weights_spp.png}
\caption{Simulated changes in biomass of the focal species (black) and all other species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for focal species biomass (blue).  }
\label{fig:community-weights-spp}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.7 \textwidth] {dispersal_niche_width.png}
	\caption{(The rate of change in the weight of the temporal forecast (y-axis) depends on (A) the fraction of propagules dispersing in the community turnover example and (B) on the temperature tolerance of genotypes, given by $\sigma_T$ (larger values indicate wider thermal niches) in the eco-evolutionary example. }
	\label{fig:dispersal_niche_width}
\end{figure}

@@

\section{Spatial and temporal models for the community turnover example}\label{metacomm}

[How much detail to include from Alexander et al?]

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_change_plus_weights_total.png}
\caption{Simulated changes in biomass all species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for total biomass (blue).  }
\label{fig:community-weights-total}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {forecast_supplement.png}
\caption{Simulated shifts in genotype abundances, and the model weighting term, $\omega$, during the warming phase and the following stationary temperature phase.}
\label{fig:forecast_supp}
\end{figure}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_change_plus_weights_spp.png}
\caption{Simulated changes in biomass of the focal species (black) and all other species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for focal species biomass (blue). Year 0 in this figure corresponds to the start of the temperature increase. }
\label{fig:community-weights-spp}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.7 \textwidth] {dispersal_niche_width.png}
	\caption{(The rate of change in the weight of the temporal forecast (y-axis) depends on (A) the fraction of propagules dispersing in the community turnover example and (B) on the temperature tolerance of genotypes, given by $\sigma_T$ (larger values indicate wider thermal niches) in the eco-evolutionary example. Year 0 in these figures corresponds to the start of the temperature increase. }
	\label{fig:dispersal_niche_width}
\end{figure}

@@

\section{Spatial, temporal, and combined models}\label{metacomm}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_change_plus_weights_total.png}
\caption{Simulated changes in biomass all species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for total biomass (blue). Year 0 in this figure corresponds to the start of the temperature increase. }
\label{fig:community-weights-total}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {forecast_supplement.png}
\caption{Simulated shifts in genotype abundances, and the model weighting term, $\omega$, during the warming phase and the following stationary temperature phase. Year 0 in this figure corresponds to the start of the temperature increase.}
\label{fig:forecast_supp}
\end{figure}
